Draft Exploration

### 2020-04-27 draft_exploration.Rmd
explanation for redraft round in shiny

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(tidycensus)
library(ggthemes)
library(ggplot2)
library(janitor)
library(dplyr)
library(gt)
library(readxl)
library(sf)
library(scales)
library(magrittr)
library(haven)
library(infer)
library(Lahman)
library(xml2)
library(rvest)
library(DataCombine)
library(RColorBrewer)
library(usmap)
```

@@

@@

@@

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(tidycensus)
library(ggthemes)
library(ggplot2)
library(janitor)
library(dplyr)
library(gt)
library(readxl)
library(sf)
library(scales)
library(magrittr)
library(haven)
library(infer)
library(Lahman)
library(xml2)
library(rvest)
library(DataCombine)
library(RColorBrewer)
library(usmap)
library(broom)
```

@@

```{r height_reformat, include=FALSE}

# I reformatted the height string to inches numeric

master <- master %>%
  mutate(ht = sapply(strsplit(master$ht,"-"),
        function(x){12*as.numeric(x[1]) + as.numeric(x[2])})) %>%
  mutate(ht = as.numeric(ht))
```

@@

Another important factor to consider when turning down the draft is how a
prospect's future draft stock may change. Earlier picks generally receive larger
signing bonuses, so a drop of several rounds can cost a player hundreds of
thousands of dollars of signing bonus money.

This graph shows the average change in draft rounds for unsigned high school
picks that are redrafted later on. Points above the red line indicate an
improved draft stock, while those below represent a drop. Viewing all five time
periods together, it is worth noting that the curves are gradually crossing the
y=0 line at an earlier round.

The leftward shift of this intersection means that earlier-round unsigned picks
are seeing an improvement in draft stock where they would have been expected to
drop in periods past. Additionally, later round picks are seeing a larger
improvement in draft stock than in prior periods. The large jump in draft stock
for late-round picks must be considered while keeping in mind only about 60% of
30th to 40th round picks from 2010 to 2015 were redrafted at all.

@@

```{r}
regression_master <- master %>%
  filter(source == "H" & draft_numb == 1) %>%
  filter(year <= 2012) %>%
  mutate(mlb_made = ifelse(high_level == "MLB", 1, 0)) %>%
  mutate(mlb_made = as.factor(mlb_made))

model_mlb_made <- glm(mlb_made ~ signed, family = binomial, data = regression_master)  %>%
  tidy(conf.int = TRUE)
